

% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.75in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% Makes resume-specific commands available.
\usepackage{resume}




\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{Javin Lacson}{}{Last update on \today}

\nobreakvspace{0.3em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:work.at.javin.io}{work\mbox{}@\mbox{}javin.io}\sbull
\textsmaller415.264.0616\sbull
\href{https://www.javin.io}{https://www.javin.io}\sbull
2340 Robert St\sbull
New Orleans, LA

\spacedhrule{0.6em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Summary}  % a root section title

\vspace{-1.3em}  % some vertical spacing
\begin{multicols}{2}  % open a multicolumn environment
\noindent \emph{Talented engineer with a passion for software development in large capacity, secure, performant, \& highly available environments. Able to consistently deliver optimized technology solutions within required business context. }
\vspace{0.3em}
\\
{During his early years, Javin taught himself programming on a TI-99, learned assembly on the C64 from printed manuals, and published numerous articles in computer magazines. He wrote the adventure game Eye of Levata in {\textsc{Basic}} \& 6502 assembly utilizing interrupts to simulate multi-threading.
}

{While obtaining his Computer Science degree, he gained a variety of skills including full stack web development and at-scale operations. During his career, he lived and worked in San Francisco for both startups and tech giants on real-time, security sensitive applications. Now back in New Orleans with his family, he is excited to bring the silicon valley fairy dust to his hometown. }

\end{multicols}


\spacedhrule{0em}{-0.5em}

\roottitle{Experience}

\headedsection
  {\href{http://www.javin.io}{Self Employed }}
  {\textsc{San Francisco Bay Area}} {
  \headedsubsection
    {Sr. Software Engineer}
    {Jul \apo17 -- Jul \apo19}
    {\bodytext{Full stack software engineering, devops, and consulting for applications in security sensitive environments. Develop software with Javascript, Ruby, Elixir, and Java satisfying {\textsc{Itar}}, {\textsc{Ear}}, {\textsc{Hipaa}}, {\textsc{Nist/Sans}}. Clients:\@ {Curie}, {Fabrix Health}, {ShireCare}, {Drop In}, {American English}, \& {TutorCorps}.}}
}

\headedsection
  {\href{http://www.google.com}{Google}}
  {\textsc{Mountain View, CA}} {%
  \headedsubsection
    {Developer Operations Engineer}
    {Aug \apo14 -- Jun \apo17}
    {\bodytext{Build and manage the secure {\textsc{Itar/Ear}} private and cloud operations infrastructure supporting image processing over petabyte-sized data sets with real-time requirements. Create multi-tenant, load balanced, security compliant cloud architecture for application development and real-time operations using Ansible, Docker, Ruby/Rails, Python/Django, and internal Google tools.  }}
}

\headedsection
  {{Skybox Imaging}}
  {\textsc{Mountain View, CA}} {
  \headedsubsection
    {Developer Operations Engineer}
    {Jun \apo11 -- Aug \apo14}
    {\bodytext{Build and manage software and infrastructure automation for spacecraft development, launch, and flight including security, communications, compliance, and devops worldwide.  } }
}

\headedsection
  {{Vertical Response}}
  {\textsc{San Francisco, CA}} {
  \headedsubsection
    {Systems Engineer}
    {May \apo07 -- Jun \apo11}
    {\bodytext{Build, scale, and manage infrastructure for Ruby/Rails application powering a SaaS platform with billions of annual transactions.  Scaled platform from 93k to 800k users with > 99.9\% availability. } }
}


\headedsection
  {{Metaweb Technologies}}
  {\textsc{San Francisco, CA}} {
  \headedsubsection
    {Systems Engineer}
    {Oct \apo04 -- May \apo07}
    {\bodytext{Developed distributed computing software for data processing applications to create a semantic web. } }
}

\vspace{0.4em}

\spacedhrule{-0.2em}{-0.4em}

\roottitle{Education}

\headedsection
  {\href{http://www.tulane.edu}{Tulane University}}
  {\textsc{New Orleans, LA}} {
  \headedsubsection
    {Bachelor of Science, Computer Science}
    {}
    {\bodytext{}}
}
\vspace{-1.4em}
\headedsection
  {\href{http://www.ccsf.edu}{City College of San Francisco}}
  {\textsc{San Francisco, CA}} {
  \headedsubsection
    {Mathematics Concentration \textnormal}
    {}
    {\bodytext{}}
}

\vspace{-1.1em}

\spacedhrule{0.5em}{-0.4em}

\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Software:}
  {Can write Elixir, Ruby, Java, Python, \LaTeX, {\textsc{Lisp}}, 6510 assembly, \& Javascript 
  \textnormal{\textit{~(in order of preference)}}. Full stack engineer with preference of Postgres, Apollo, React, & SSR. Especially enjoy back-end, data modeling, scaling, security, and {\textsc{Api}} development. Unique ability to bring idea from concept to completion. }

\vspace{0.4em}
\inlineheadsection
  {Operations:}  
  {Linux Wizard. Agile methodologies, Kanban/Scrum, continuous delivery (Jenkins, Jira, Ansible, Puppet), Ops infra (Cisco, Netapp, Juniper, Barracuda, F5), virtualization (Vmware, Docker, Kubernetes, Xen, OpenVZ), \& cloud platforms (Google, {\textsc{Aws}}, Digital Ocean). Emacs power user.}

\vspace{0.4em}
\inlineheadsection
  {Business:}
  {Creating high performance culture, recruitment, corporate governance, security, compliance, due diligence, M\&A, interviewing, re-organizations, contracting, financial/project estimation, \& outsourcing. }

\spacedhrule{1.6em}{-0.5em}

\roottitle{Interests}

\inlineheadsection
  {In no particular order:}
  {private pilot, college wrestler, rock climber, river kayaker, adventure guide, wilderness first responder, mathematician, entrepreneur, real estate investor, functional programmer, coach, tutor, mentor, woodworker, tinkerer, and most of all 7 wonders duel pantheon expert. }

\end{document}
